---
title: "R Project 1 - Hello R"
author: "Sharrah Allen-Benson"
date: "9/16/2020"
output: 
  html_document: 
    theme: cosmo
    highlight: haddock
  pdf_document: 
    highlight: espresso
---

## Loaded packages:

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
library(magrittr)
library(ggplot2)
library(rlang)
```


## Exercise 1

#### The datasaurus_dozen file has 1846 rows and 3 columns, or variables. The variables included in the data frame are the x-values, y-values, and dataset. 



## Exercise 2: dino_data

#### Here is dino_data plotted:  

```{r plot-dino, fig.height=7, fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#### Here is the code to calculate the correlation coefficient between x and y for this dataset:



```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
* The correlation coefficient is -0.0645.

## Exercise 3: star_data

#### Here is star_data plotted:

```{r plot-star, fig.height=7, fig.width=7}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

#### Here is the code to calculate the correlation coefficient between x and y for this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
* The correlation coefficient is -0.0630. Compared to the correlation coefficient of dino_data, -0.0645, this correlation coefficient of -0.0630 is greater than the *r* of dino_data by 0.0015.

## Exercise 4: circle_data

#### Here is circle_data plotted:

```{r plot-circle, fig.height=7, fig.width=7}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

#### Here is the code to calculate the correlation coefficient between x and y for this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))


```
* The correlation coefficient is -0.0683. Compared to the correlation coefficient of dino_data, -0.0645, this correlation coefficient of -0.0683 is less than the *r* of dino_data by 0.0038.

## Exercise 5: datasaurus_dozen

#### Here is all datasets in datasaurus_data plotted:

```{r plot- datasaurus_dozen, fig.height=15, fig.width=15}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + 
theme(legend.position = "none")

```

#### Here is the code to calculate the correlation coefficient between x and y for all datasets in datasaurus_data: 

```{r cor-datasaurus_dozen}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)

```

