---
title: "R Project 1 - Hello R"
author: "Sharrah Allen-Benson"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

**Answer**: The **datasaurus_dozen** file has 1846 rows and 3 columns, or variables. The variables included in the data frame are the x-values, y-values, and dataset. 

### Exercise 2

**Here is dino_data plotted:**

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

**Here is the code to calculate the correlation coefficient between x and y for this dataset:**

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
**The correlation coefficient is -0.0645.**

## Exercise 3: star_data

**Here is star_data plotted:**

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

**Here is the code to calculate the correlation coefficient between x and y for this dataset:**
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
* The correlation coefficient is -0.0630. Compared to the correlation coefficient of dino_data, -0.0645, this correlation coefficient of -0.0630, is greater than the *r* of dino_data by 0.0015.

## Exercise 4: circle_data

##### Here is circle_data plotted:

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

##### Here is the code to calculate the correlation coefficient between x and y for this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))


```
* The correlation coefficient is -0.0683. Compared to the correlation coefficient of dino_data, -0.0645, this correlation coefficient of -0.0683, is less than the *r* of dino_data by 0.0038.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)